---
title: "11-Load-Rescue-Data"
output: html_notebook
---


CSV import - *Mac*
*change input file path*
```{r}
testdata=read.csv(file="~/Desktop/29Jun21_analysis/NSW3017_basal_counts_29Jun21.csv",header=TRUE)
testdata$BvsS<-"Basal"
testdata$BafA<-"BafAN"
testdata$Rep<-4
nobs=nrow(testdata)
for (i in 1:nobs) {
  if (testdata[i,1]=="") {
    testdata[i,1]<-fname

  } 
  else {
    fname=testdata[i,1]

  }
}

```


CSV import - *Windows*
*MUST HAVE FILES IN R PROJECT WD* 
*change input file path*
```{r}
temp=read.csv(file="./rescue-analysis_22May22/datasets/NSW4040_21May22.csv",header=TRUE)
temp$BvsS<-"Basal"
temp$Rep<-1
nobs=nrow(temp)
for (i in 1:nobs) {
  if (temp[i,1]=="") {
    temp[i,1]<-fname

  } 
  else {
    fname=temp[i,1]

  }
}

```

Adding type designation
*if necessary update substring values based on filename in input document*
*check capitalization of values*
```{r}
temp$Type<-NA
ntemp<-nrow(temp)


for (c in 1:ntemp) {
  if (substr(temp[c,1],34,34)=="W") {
    temp$Type[c]<-"WT"
  }
  else if (substr(temp[c,1],34,34)=="C") {
    temp$Type[c]<-"Control"
  }
  else {
    temp$Type[c]<-"tepsin"
  }
  
}
temp$Type<-factor(temp$Type, levels=c("WT", "Control", "tepsin"))
```


Adding rescue designation
*if necessary update substring values based on filename in input document*
*check capitalization of values*
```{r}
temp$Rescue<-NA
ntemp<-nrow(temp)


for (c in 1:ntemp) {
  if (substr(temp[c,1],36,38)=="000") {
    temp$Rescue[c]<-"unt"
  }
  else if (substr(temp[c,1],36,38)=="087") {
    temp$Rescue[c]<-"WTtep"
  }
    else if (substr(temp[c,1],36,38)=="088") {
    temp$Rescue[c]<-"LIRless"
  }
  else {
    temp$Rescue[c]<-"Cterm"
  }
  
}
temp$Rescue<-factor(temp$Rescue, levels=c("unt", "WTtep", "LIRless", "Cterm"))
```





#Logic checks to ensure data is used only from properly segmented cells
Find files where number of Nuclei in segmented cells does not match number of segmented cells:

These files should be evaluated to identify images where cells were not segmented properly. 

```{r}
ntemp<-nrow(temp)
temp[,2]<-as.numeric(temp[,2])
temp[,3]<-as.numeric(temp[,3])
rs<-c()

for (i in 1:ntemp) {
  if (!is.na(temp[i,2]) & temp[i,2]!=temp[i,3]) {
      rs<-c(rs,i)
    }
  
}

badcell1<-data.frame(temp[rs,])
```

Checking for images where the number of cells with MOC measurements does not match the number of counted cells to validated cell segmentation. All cells should have MOC measurements while not all will have puncta measurements
```{r}
ntemp<-nrow(temp)
temp[,2]<-as.numeric(temp[,2])
temp[,4]<-as.numeric(temp[,4])
ncell<-temp[1,2]
rs<-c()

for (i in 1:ntemp) {
  if (!is.na(temp[i,2]) & i!=1) {
    if (!is.na(temp[i-1,4]) & ncell!=temp[i-1,4]) {
      rs<-c(rs,i-1)
    }
    ncell<-temp[i,2]
  }
  
  if (i==ntemp){
    if (!is.na(temp[i,4]) & ncell!=temp[i,4]) {
      rs<-c(rs,i)
    }
  }
}

badcell2<-data.frame(temp[rs,])
```


#Find max mean Myc value of untransfected cells
Adjust transfected threshold value based on this max
```{r}
print(max(temp$meanMyc[which(temp$Rescue=="unt")]))
```


#Identify transfected cells using Myc signal intensity values

Subset whole cell values and add transfected designation
Need to add a way to subset dataset to include only transfected cells from conditions other than untransfected (000)
*add binary designation Yes/No for cells to include*
```{r}
#whole cell subset
whole<-temp[which(!is.na(temp$CellID)),c(1:11,22:25)]

whole$include<-NA
ntemp<-nrow(whole)

for (c in 1:ntemp) {
  if (substr(whole[c,1],38,38)=="0") {
    whole$include[c]<-"Y"
  }
  else if (whole$meanMyc[c]>165) {
    whole$include[c]<-"Y"
  }
    
  else {
    whole$include[c]<-"N"
    
  }
}
```




For individual cell value metrics
```{r}
ntemp<-nrow(temp)


rs2<-temp[which(temp$meanMyc>165),c(1,4,6)]

rs2$pCell<-rs2$CellID
rs2$pCellmean<-rs2$meanMyc
rs2<-rs2[,c(-2,-3)]


included<-merge(temp,rs2,by=c("Filename","pCell"),all.x = TRUE)


rs3<-rs2
rs3$gCell<-rs2$pCell
rs3$gCellmean<-rs2$pCellmean
rs3<-rs3[,c(-2,-3)]

included<-merge(included,rs3,by=c("Filename","gCell"),all.x = TRUE)
included$include<-NA

for (c in 1:ntemp) {
  if (substr(included[c,1],36,38)=="000") {
    included$pinclude[c]<-"Y"
  }
  else if (!is.na(included$pCellmean[c]) && included$pCellmean[c]>180)
 {
    included$pinclude[c]<-"Y"
  }
    
  else {
    included$pinclude[c]<-"N"
  }
    if (substr(included[c,1],36,38)=="000") {
    included$ginclude[c]<-"Y"
  }
  else if (!is.na(included$gCellmean[c]) && included$gCellmean[c]>180)
 {
    included$ginclude[c]<-"Y"
  }
    
  else {
    included$ginclude[c]<-"N"
  }
}


```


Individual pCell gCell metrics tidy dataset
```{r}
pDat<-NA
pDat<-included[,c(1,22,23,24,25,3,26,29,16,17,18)]

gDat<-NA
gDat<-included[,c(1,22,23,24,25,2,27,30,19,20,21)]
```


#Subset datasets to exclude cells in transfected treatments without Myc signal

```{r}

#whole cell dataset
wTidy<-whole[whole$include== "Y",]

#individual nonGolgi metric dataset
pTidy<-pDat[pDat$pinclude == "Y",]

#individual Golgi metric dataset
gTidy<-gDat[gDat$ginclude == "Y",]
```


#Data calculation operations

Get Sum of cell counts per type
```{r}
wTidy$CellSum<-NA
ntemp<-nrow(wTidy)

for (t in c("WT", "Control", "tepsin")) {
  for (tr in c("unt", "WTtep", "LIRless", "Cterm")) {
    for (r in c("1", "2","3", "4")) {
       wTidy$CellSum[which(wTidy$Type==t & wTidy$Rescue==tr & wTidy$Rep==r)]<-sum(wTidy$SegCellCount[which(wTidy$Type==t & wTidy$Rescue==tr & wTidy$Rep==r)],na.rm = TRUE)
      }
    }
  }
```


Calculate the ratio of Golgi localized ATG9A relative to whole cell measurement
```{r}
wTidy$PercGolATG9<-NA
ntemp<-nrow(wTidy)

for (i in 1:ntemp) {
  wTidy[i,18]<-(wTidy[i,7]/wTidy[i,8])*100
}
```


#If cell average values are desired
*THIS NEEDS TO BE ADJUSTED FOR RESCUE DATAFRAME*

Getting average values per cell for non-Golgi ATG9 object volume and non-Golgi object max intensity

```{r}

ntemp<-nrow(temp)
temp[,14]<-as.numeric(temp[,14])
temp$AveATG9VolPerCell <- NA
temp$AveATG9MaxIntPerCell <- NA

rs<-c()
cid<-1
fname<-temp[1,1]
for (i in 1:ntemp) {
  if (!is.na(temp[i,14])){
    if (temp[i,14]!=cid | temp[i,1]!=fname) {
      temp$AveATG9VolPerCell[rs]<-mean(temp$nonGolATG9Vol[rs])
      temp$AveATG9MaxIntPerCell[rs]<-mean(temp$nonGolATG9MaxInt[rs])
      rs<-c(i)
      cid<-temp[i,14]
      fname<-temp[i,1]
    }
    else {
      rs<-c(rs,i)
    }
  }
  if (i==ntemp){
    temp$AveATG9VolPerCell[rs]<-mean(temp$nonGolATG9Vol[rs])
    temp$AveATG9MaxIntPerCell[rs]<-mean(temp$nonGolATG9MaxInt[rs])
  }
}
```

Getting average values per cell for Golgi ATG9 object max intensity
```{r}

ntemp<-nrow(temp)
temp[,18]<-as.numeric(temp[,18])
temp$AveATG9gMaxIntPerCell <- NA

rs<-c()
cid<-1
fname<-temp[1,1]
for (i in 1:ntemp) {
  if (!is.na(temp[i,18])){
    if (temp[i,18]!=cid | temp[i,1]!=fname) {
      temp$AveATG9gMaxIntPerCell[rs]<-mean(temp$GolATG9MaxInt[rs])
      rs<-c(i)
      cid<-temp[i,18]
      fname<-temp[i,1]
    }
    else {
      rs<-c(rs,i)
    }
  }
  if (i==ntemp){
    temp$AveATG9gMaxIntPerCell[rs]<-mean(temp$GolATG9MaxInt[rs])
  }
}
```




Removing unnecessary columns and duplicate rows to have values per cell
*non-Golgi ATG9 metrics; also renames CellID column to prepare for merging*
```{r}
nonGolginoDup<-temp[!duplicated(temp[,c(1,14,28)]),c(1,14,25,26,27,29,30,31)]
nonGolginoDup<-nonGolginoDup[which(!is.na(nonGolginoDup[,2])),]
names(nonGolginoDup)[names(nonGolginoDup)=="pCell"]<-"sCellID"
```

Removing unnecessary columns and duplicate rows to have values per cell
*Golgi ATG9a max int; also renames CellID column to prepare for merging*
```{r}
GolginoDup<-temp[!duplicated(temp[,c(1,21,32)]),c(1,21,25,26,27,32)]
GolginoDup<-GolginoDup[which(!is.na(GolginoDup[,2])),]
names(GolginoDup)[names(GolginoDup)=="gCell"]<-"sCellID"
```

Merging nonGolgi and Golgi cleaned data frames for graphing
```{r}
tidy <- merge(nonGolginoDup,GolginoDup, all = TRUE)
```


