---
title: "30-Statistical-Analysis"
output: html_notebook
---
*For data subsetting*
```{r}
#Subset data by replicate
#rename dataframes as needed and adjust rbinds
rep12wTidy<-rbind(rep1wTidy,rep2wTidy)
rep12pTidy<-rbind(rep1pTidy,rep2pTidy)
rep12gTidy<-rbind(rep1gTidy,rep2gTidy)
```

#use to run within Type comparisons, otherwise load comb dataframes of desired replicates for subsetting rescue type
```{r}
#Subset data by Type for within type comparisons moving forward
combwTidy<-rep12wTidy[rep12wTidy$Type=="WT",]
combpTidy<-rep12pTidy[rep12pTidy$Type=="WT",]
combgTidy<-rep12gTidy[rep12gTidy$Type=="WT",]
```

#check that combined dataframes have desired datasets
```{r}
#Subset data by rescue type and run individually
resCwTidy<-combwTidy[combwTidy$Rescue=="unt",]
resCpTidy<-combpTidy[combpTidy$Rescue=="unt",]
resCgTidy<-combgTidy[combwTidy$Rescue=="unt",]
```

Kruskal-Wallis Test of metrics; separate Basal vs Starved analysis
*NONPARAMETRIC DATA**multiple replicates*
```{r}

#install.packages("tidyverse")
#install.packages("ggpubr")
#install.packages("rstatix")
#library(tidyverse)
#library(ggpubr)
#library(rstatix)

KW_M1<-kruskal_test(MandersM1~Type, data=resCwTidy)
summary(KW_M1)
dt_M1<-dunn_test(MandersM1~Type, data=resCwTidy, p.adjust.method = "bonferroni")

KW_M2<-kruskal_test(MandersM2~Type, data=resCwTidy)
summary(KW_M2)
dt_M2<-dunn_test(MandersM2~Type, data=resCwTidy, p.adjust.method = "bonferroni")

KW_MOC<-kruskal_test(MandersMOC~Type, data=resCwTidy)
summary(KW_MOC)
dt_MOC<-dunn_test(MandersMOC~Type, data=resCwTidy, p.adjust.method = "bonferroni")

KW_PCC<-kruskal_test(PearsonCoeff~Type, data=resCwTidy)
summary(KW_PCC)
dt_PCC<-dunn_test(PearsonCoeff~Type, data=resCwTidy, p.adjust.method = "bonferroni")

KW_nonGolVol<-kruskal_test(nonGolATG9Vol~Type, data=resCpTidy)
summary(KW_nonGolVol)
dt_nonGolVol<-dunn_test(nonGolATG9Vol~Type, data=resCpTidy, p.adjust.method = "bonferroni")

KW_nonGolMaxInt<-kruskal_test(nonGolATG9MaxInt~Type, data=resCpTidy)
summary(KW_nonGolMaxInt)
dt_nonGolMaxInt<-dunn_test(nonGolATG9MaxInt~Type, data=resCpTidy, p.adjust.method = "bonferroni")

KW_GolMaxInt<-kruskal_test(GolATG9MaxInt~Type, data=resCgTidy)
summary(KW_GolMaxInt)
dt_GolMaxInt<-dunn_test(GolATG9MaxInt~Type, data=resCgTidy, p.adjust.method = "bonferroni")

#KW_nonGolMaxIntCell<-kruskal_test(AveATG9MaxIntPerCell~Type, data=tidy)
#summary(KW_nonGolMaxIntCell)
#dt_nonGolMaxIntCell<-dunn_test(AveATG9MaxIntPerCell~Type, data=tidy, p.adjust.method = "bonferroni")

#KW_nonGolVolCell<-kruskal_test(AveATG9VolPerCell~Type, data=tidy)
#summary(KW_nonGolVolCell)
#dt_nonGolVolCell<-dunn_test(AveATG9VolPerCell~Type, data=tidy, p.adjust.method = "bonferroni")

#KW_GolMaxIntCell<-kruskal_test(AveATG9gMaxIntPerCell~Type, data=tidy)
#summary(KW_GolMaxIntCell)
#dt_GolMaxIntCell<-dunn_test(AveATG9gMaxIntPerCell~Type, data=tidy, p.adjust.method = "bonferroni")



```


R-bind and export results from Kruskal-Wallis and Dunn test
```{r}
Dunn_ATG9rescue<-rbind(dt_M1,dt_M2,dt_MOC,dt_PCC,dt_nonGolVol,dt_nonGolMaxInt,dt_GolMaxInt#,dt_nonGolMaxIntCell,dt_nonGolVolCell,dt_GolMaxIntCell
                 )



write.csv(Dunn_ATG9rescue, file= "./stats/ATG9A-rescues/Dunn_ATG9-rescue-unt_4046-4048-4049_20Nov22.csv")

```


Analysis of Percent Golgi ATG9A signal
*make sure temp dataset is subset and cleaned data*
```{r}
KW_PGATG9<-kruskal_test(PercGolATG9~Type, data=temp)
summary(KW_PGATG9)
dt_PGATG9<-dunn_test(PercGolATG9~Type, data=temp, p.adjust.method = "bonferroni")

write.csv(dt_PGATG9, file= "./stats/PercGolATG9_May2023/Dunn_PercGolATG9_4019-4020-4022-4026_15May23.csv")
```



U-Test of MOC
*for nonparametric distributions*


*Optional to subset data*
```{r}
subsetC<-tidy[tidy$Type == "Control",]
subsetT<-tidy[tidy$Type == "tepsin",]


subsetconUC<-subsetC[subsetC$Rescue == "unt" | subsetC$Rescue == "Cterm",]
subsettepUC<-subsetT[subsetT$Rescue == "unt" | subsetT$Rescue == "Cterm",]


```

```{r}

ConMandersUtest<-wilcox_test(data=subsetC, MandersMOC ~ Rescue, paired= FALSE)

TepMandersUtest<-wilcox_test(data=subsetT, MandersMOC ~ Rescue, paired= FALSE)

MandersUtest<-rbind(ConMandersUtest,TepMandersUtest)
write.csv(MandersUtest, file= "./stats/ATG9A-rescues/Utest_ATG9-rescue_4046-4048-4049_20Nov22.csv")

```

